---
title: "Multi / WebExtensions Telemetry Performance"
output: 
  html_document:
  theme: cosmo
---












# Results {.tabset .tabset-fade }


## week4 {.tabset .tabset-fade }

The data shows the following concerns based on histogram comparisons:

```{r, echo=FALSE}
#htmltools::includeHTML('./week4/html/concerns.html')
```

<br>

### Dataset Summary

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/summary.html')
```
  
### Probes {.tabset .tabset-fade}

#### Jank {.tabset .tabset-fade .tabset-pills}

##### GC_MAX_PAUSE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/GC_MAX_PAUSE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/GC_MAX_PAUSE_MS4+-Tabs.html')
```

##### CYCLE_COLLECTOR_MAX_PAUSE {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/CYCLE_COLLECTOR_MAX_PAUSE1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/CYCLE_COLLECTOR_MAX_PAUSE4+-Tabs.html')
```

##### INPUT_EVENT_RESPONSE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/INPUT_EVENT_RESPONSE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/INPUT_EVENT_RESPONSE_MS4+-Tabs.html')
```

#### Tab Switching {.tabset .tabset-fade .tabset-pills}

##### FX_PAGE_LOAD_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_PAGE_LOAD_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_PAGE_LOAD_MS4+-Tabs.html')
```


##### FX_TAB_REMOTE_NAVIGATION_DELAY_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_REMOTE_NAVIGATION_DELAY_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_REMOTE_NAVIGATION_DELAY_MS4+-Tabs.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS4+-Tabs.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_MS4+-Tabs.html')
```
##### FX_TAB_SWITCH_TOTAL_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_TOTAL_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_TOTAL_MS4+-Tabs.html')
```

##### FX_TAB_SWITCH_UPDATE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_UPDATE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_UPDATE_MS4+-Tabs.html')
```

#### Memory Usage {.tabset .tabset-fade .tabset-pills}

##### MEMORY_DISTRIBUTION_AMONG_CONTENT {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_DISTRIBUTION_AMONG_CONTENT1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_DISTRIBUTION_AMONG_CONTENT4+-Tabs.html')
```

##### MEMORY_TOTAL {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_TOTAL1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_TOTAL4+-Tabs.html')
```

##### MEMORY_VSIZE_MAX_CONTIGUOUS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_VSIZE_MAX_CONTIGUOUS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_VSIZE_MAX_CONTIGUOUS4+-Tabs.html')
```
#### Slow Scripts {.tabset .tabset-fade .tabset-pills}

##### SLOW_SCRIPT_NOTICE_COUNT {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTICE_COUNT1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTICE_COUNT4+-Tabs.html')
```

##### SLOW_SCRIPT_PAGE_COUNT {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_PAGE_COUNT1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_PAGE_COUNT4+-Tabs.html')
```

##### SLOW_SCRIPT_NOTIFY_DELAY {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTIFY_DELAY1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTIFY_DELAY4+-Tabs.html')
```

### Stacks {.tabset .tabset-fade .tabset-pills}

<br>

Here we look for major stack differences between cohorts. The stacks are sorted by frequency in the left most column which corresponds to the selected tab. For example, in the `webextensions-multiBucket1` tab, the left most column are the top 25 most occuring stacks in that cohort. The percentages for the other cohorts are included for comparison. For each row, if a cell in the left most column is noticeably darker than cells to its right, then that cohort may have a hangs issue. 

<br>


#### webextensions-multiBucket1
```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/wm1.html')
```

#### webextensions-multiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/wm4.html')
```

#### MultiBucket1

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/m1.html')
```


#### MultiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/m4.html')
```

#### MPC1

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/mpc1.html')
```

#### MPC4

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/mpc4.html')
```


## week3 {.tabset .tabset-fade }

The data shows the following concerns based on histogram comparisons:

```{r, echo=FALSE}
#htmltools::includeHTML('./week3/html/concerns.html')
```

<br>

### Dataset Summary

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/summary.html')
```
  
### Probes {.tabset .tabset-fade}

#### Jank {.tabset .tabset-fade .tabset-pills}

##### GC_MAX_PAUSE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/GC_MAX_PAUSE_MS.html')
```

##### CYCLE_COLLECTOR_MAX_PAUSE

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/CYCLE_COLLECTOR_MAX_PAUSE.html')
```

##### INPUT_EVENT_RESPONSE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/INPUT_EVENT_RESPONSE_MS.html')
```

#### Tab Switching {.tabset .tabset-fade .tabset-pills}

##### FX_PAGE_LOAD_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/FX_PAGE_LOAD_MS.html')
```


##### FX_TAB_REMOTE_NAVIGATION_DELAY_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/FX_TAB_REMOTE_NAVIGATION_DELAY_MS.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/FX_TAB_SWITCH_SPINNER_VISIBLE_MS.html')
```

##### FX_TAB_SWITCH_TOTAL_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/FX_TAB_SWITCH_TOTAL_MS.html')
```

##### FX_TAB_SWITCH_UPDATE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/FX_TAB_SWITCH_UPDATE_MS.html')
```

#### Memory Usage {.tabset .tabset-fade .tabset-pills}

##### MEMORY_DISTRIBUTION_AMONG_CONTENT

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/MEMORY_DISTRIBUTION_AMONG_CONTENT.html')
```

##### MEMORY_TOTAL

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/MEMORY_TOTAL.html')
```

##### MEMORY_VSIZE_MAX_CONTIGUOUS

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/MEMORY_VSIZE_MAX_CONTIGUOUS.html')
```

#### Slow Scripts {.tabset .tabset-fade .tabset-pills}

##### SLOW_SCRIPT_NOTICE_COUNT

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/SLOW_SCRIPT_NOTICE_COUNT.html')
```

##### SLOW_SCRIPT_PAGE_COUNT

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/SLOW_SCRIPT_PAGE_COUNT.html')
```

##### SLOW_SCRIPT_NOTIFY_DELAY

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/SLOW_SCRIPT_NOTIFY_DELAY.html')
```


### Stacks {.tabset .tabset-fade .tabset-pills}

<br>

Here we look for major stack differences between cohorts. The stacks are sorted by frequency in the left most column which corresponds to the selected tab. For example, in the `webextensions-multiBucket1` tab, the left most column are the top 25 most occuring stacks in that cohort. The percentages for the other cohorts are included for comparison. For each row, if a cell in the left most column is noticeably darker than cells to its right, then that cohort may have a hangs issue. 

<br>


#### webextensions-multiBucket1
```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/wm1.html')
```

#### webextensions-multiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/wm4.html')
```

#### MultiBucket1

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/m1.html')
```


#### MultiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/m4.html')
```


#### MPC-1

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/mpc1.html')
```

#### MPC-4

```{r, echo=FALSE}
htmltools::includeHTML('./week3/html/mpc4.html')
```






## week2 {.tabset .tabset-fade }

The data shows the following concerns based on histogram comparisons:

```{r, echo=FALSE}
#htmltools::includeHTML('./data/week2/concerns.html')
```

<br>

### Dataset Summary

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/summary.html')
```
  
### Probes {.tabset .tabset-fade}

#### Jank {.tabset .tabset-fade .tabset-pills}

##### GC_MAX_PAUSE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/GC_MAX_PAUSE_MS.html')
```

##### CYCLE_COLLECTOR_MAX_PAUSE

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/CYCLE_COLLECTOR_MAX_PAUSE.html')
```

##### INPUT_EVENT_RESPONSE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/INPUT_EVENT_RESPONSE_MS.html')
```

#### Tab Switching {.tabset .tabset-fade .tabset-pills}

##### FX_PAGE_LOAD_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/FX_PAGE_LOAD_MS.html')
```


##### FX_TAB_REMOTE_NAVIGATION_DELAY_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/FX_TAB_REMOTE_NAVIGATION_DELAY_MS.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/FX_TAB_SWITCH_SPINNER_VISIBLE_MS.html')
```

##### FX_TAB_SWITCH_TOTAL_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/FX_TAB_SWITCH_TOTAL_MS.html')
```

##### FX_TAB_SWITCH_UPDATE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/FX_TAB_SWITCH_UPDATE_MS.html')
```

#### Memory Usage {.tabset .tabset-fade .tabset-pills}

##### MEMORY_DISTRIBUTION_AMONG_CONTENT

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/MEMORY_DISTRIBUTION_AMONG_CONTENT.html')
```

##### MEMORY_TOTAL

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/MEMORY_TOTAL.html')
```

##### MEMORY_VSIZE_MAX_CONTIGUOUS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/MEMORY_VSIZE_MAX_CONTIGUOUS.html')
```

#### Slow Scripts {.tabset .tabset-fade .tabset-pills}

##### SLOW_SCRIPT_NOTICE_COUNT

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/SLOW_SCRIPT_NOTICE_COUNT.html')
```

##### SLOW_SCRIPT_PAGE_COUNT

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/SLOW_SCRIPT_PAGE_COUNT.html')
```

##### SLOW_SCRIPT_NOTIFY_DELAY

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/SLOW_SCRIPT_NOTIFY_DELAY.html')
```


### Stacks {.tabset .tabset-fade .tabset-pills}

<br>

Here we look for major stack differences between cohorts. The stacks are sorted by frequency in the left most column which corresponds to the selected tab. For example, in the `webextensions-multiBucket1` tab, the left most column are the top 25 most occuring stacks in that cohort. The percentages for the other cohorts are included for comparison. For each row, if a cell in the left most column is noticeably darker than cells to its right, then that cohort may have a hangs issue. 

<br>


#### webextensions-multiBucket1
```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/wm1.html')
```

#### webextensions-multiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/wm4.html')
```

#### MultiBucket1

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/m1.html')
```


#### MultiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./data/week2/m4.html')
```









# Results {.tabset .tabset-fade }


## week4 {.tabset .tabset-fade }

The data shows the following concerns based on histogram comparisons:

```{r, echo=FALSE}
#htmltools::includeHTML('./week4/html/concerns.html')
```

<br>

### Dataset Summary

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/summary.html')
```
  
### Probes {.tabset .tabset-fade}

#### Jank {.tabset .tabset-fade .tabset-pills}

##### GC_MAX_PAUSE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/GC_MAX_PAUSE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/GC_MAX_PAUSE_MS4+-Tabs.html')
```

##### CYCLE_COLLECTOR_MAX_PAUSE {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/CYCLE_COLLECTOR_MAX_PAUSE1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/CYCLE_COLLECTOR_MAX_PAUSE4+-Tabs.html')
```

##### INPUT_EVENT_RESPONSE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/INPUT_EVENT_RESPONSE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/INPUT_EVENT_RESPONSE_MS4+-Tabs.html')
```

#### Tab Switching {.tabset .tabset-fade .tabset-pills}

##### FX_PAGE_LOAD_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_PAGE_LOAD_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_PAGE_LOAD_MS4+-Tabs.html')
```


##### FX_TAB_REMOTE_NAVIGATION_DELAY_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_REMOTE_NAVIGATION_DELAY_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_REMOTE_NAVIGATION_DELAY_MS4+-Tabs.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS4+-Tabs.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_SPINNER_VISIBLE_MS4+-Tabs.html')
```
##### FX_TAB_SWITCH_TOTAL_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_TOTAL_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_TOTAL_MS4+-Tabs.html')
```

##### FX_TAB_SWITCH_UPDATE_MS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_UPDATE_MS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/FX_TAB_SWITCH_UPDATE_MS4+-Tabs.html')
```

#### Memory Usage {.tabset .tabset-fade .tabset-pills}

##### MEMORY_DISTRIBUTION_AMONG_CONTENT {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_DISTRIBUTION_AMONG_CONTENT1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_DISTRIBUTION_AMONG_CONTENT4+-Tabs.html')
```

##### MEMORY_TOTAL {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_TOTAL1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_TOTAL4+-Tabs.html')
```

##### MEMORY_VSIZE_MAX_CONTIGUOUS {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_VSIZE_MAX_CONTIGUOUS1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/MEMORY_VSIZE_MAX_CONTIGUOUS4+-Tabs.html')
```
#### Slow Scripts {.tabset .tabset-fade .tabset-pills}

##### SLOW_SCRIPT_NOTICE_COUNT {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTICE_COUNT1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTICE_COUNT4+-Tabs.html')
```

##### SLOW_SCRIPT_PAGE_COUNT {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_PAGE_COUNT1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_PAGE_COUNT4+-Tabs.html')
```

##### SLOW_SCRIPT_NOTIFY_DELAY {.tabset .tabset-fade}

###### 1-3 Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTIFY_DELAY1-3Tabs.html')
```

###### 4+ Tabs

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/SLOW_SCRIPT_NOTIFY_DELAY4+-Tabs.html')
```

### Stacks {.tabset .tabset-fade .tabset-pills}

<br>

Here we look for major stack differences between cohorts. The stacks are sorted by frequency in the left most column which corresponds to the selected tab. For example, in the `webextensions-multiBucket1` tab, the left most column are the top 25 most occuring stacks in that cohort. The percentages for the other cohorts are included for comparison. For each row, if a cell in the left most column is noticeably darker than cells to its right, then that cohort may have a hangs issue. 

<br>


#### webextensions-multiBucket1
```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/wm1.html')
```

#### webextensions-multiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/wm4.html')
```

#### MultiBucket1

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/m1.html')
```


#### MultiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/m4.html')
```

#### MPC1

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/mpc1.html')
```

#### MPC4

```{r, echo=FALSE}
htmltools::includeHTML('./week4/html/mpc4.html')
```


## week1 {.tabset .tabset-fade }

The data shows the following concerns based on histogram comparisons:

```{r, echo=FALSE}
#htmltools::includeHTML('./data/week1/concerns.html')
```

<br>

### Dataset Summary

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/summary.html')
```
  
### Probes {.tabset .tabset-fade}

#### Jank {.tabset .tabset-fade .tabset-pills}

##### GC_MAX_PAUSE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/GC_MAX_PAUSE_MS.html')
```

##### CYCLE_COLLECTOR_MAX_PAUSE

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/CYCLE_COLLECTOR_MAX_PAUSE.html')
```

##### INPUT_EVENT_RESPONSE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/INPUT_EVENT_RESPONSE_MS.html')
```

#### Tab Switching {.tabset .tabset-fade .tabset-pills}

##### FX_PAGE_LOAD_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/FX_PAGE_LOAD_MS.html')
```


##### FX_TAB_REMOTE_NAVIGATION_DELAY_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/FX_TAB_REMOTE_NAVIGATION_DELAY_MS.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/FX_TAB_SWITCH_SPINNER_VISIBLE_LONG_MS.html')
```

##### FX_TAB_SWITCH_SPINNER_VISIBLE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/FX_TAB_SWITCH_SPINNER_VISIBLE_MS.html')
```

##### FX_TAB_SWITCH_TOTAL_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/FX_TAB_SWITCH_TOTAL_MS.html')
```

##### FX_TAB_SWITCH_UPDATE_MS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/FX_TAB_SWITCH_UPDATE_MS.html')
```

#### Memory Usage {.tabset .tabset-fade .tabset-pills}

##### MEMORY_DISTRIBUTION_AMONG_CONTENT

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/MEMORY_DISTRIBUTION_AMONG_CONTENT.html')
```

##### MEMORY_TOTAL

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/MEMORY_TOTAL.html')
```

##### MEMORY_VSIZE_MAX_CONTIGUOUS

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/MEMORY_VSIZE_MAX_CONTIGUOUS.html')
```

#### Slow Scripts {.tabset .tabset-fade .tabset-pills}

##### SLOW_SCRIPT_NOTICE_COUNT

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/SLOW_SCRIPT_NOTICE_COUNT.html')
```

##### SLOW_SCRIPT_PAGE_COUNT

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/SLOW_SCRIPT_PAGE_COUNT.html')
```

##### SLOW_SCRIPT_NOTIFY_DELAY

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/SLOW_SCRIPT_NOTIFY_DELAY.html')
```


### Stacks {.tabset .tabset-fade .tabset-pills}

<br>

Here we look for major stack differences between cohorts. The stacks are sorted by frequency in the left most column which corresponds to the selected tab. For example, in the `webextensions-multiBucket1` tab, the left most column are the top 25 most occuring stacks in that cohort. The percentages for the other cohorts are included for comparison. For each row, if a cell in the left most column is noticeably darker than cells to its right, then that cohort may have a hangs issue. 

<br>


#### webextensions-multiBucket1
```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/wm1.html')
```

#### webextensions-multiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/wm4.html')
```

#### MultiBucket1

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/m1.html')
```


#### MultiBucket4

```{r, echo=FALSE}
htmltools::includeHTML('./data/week1/m4.html')
```
